An Improved ANS Transaction Template

### 2018-01-27 paper.tex
removing flow equation

The second step determines how to populate the cascade with the user-defined
maximum number of centrifuges. One first solves the linear flow equation to
determine the theoretical flow in the cascade:

\begin{strip}
\begin{equation}
\setcounter{MaxMatrixCols}{20}
\begin{bmatrix}
-1         & 1-\theta_{S+1} & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & 0            & 0 \\
\theta_{S} & -1             & 1-\theta_{S+2} & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & 0            & 0 \\
           &                &                &   &     &   &              & ... &                &   &     &              &              &   \\
0          & 0              & 0              & 0 & ... & 0 & \theta_{-1}  & -1  & 1 - \theta_{1} & 0 & ... & 0            & 0            & 0 \\
           &                &                &   &     &   &              & ... &                &   &     &              &              &   \\
0          & 0              & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & \theta_{E-2} & -1           & 1-\theta_{E} \\
0          & 0              & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & \theta_{E-1} & -1
\end{bmatrix}
\times
\begin{bmatrix}
     F_{S}   \\
     F_{S+1} \\
     \cdots  \\
     F_{0}   \\
    \cdots   \\
    F_{E-1}  \\
    F_{E}
\end{bmatrix}
=
\begin{bmatrix}
     0   \\
     0 \\
     \cdots  \\
     F   \\
    \cdots   \\
    0  \\
    0
\end{bmatrix}
%\caption{caption needed!}
\label{eq:flow}
\end{equation}
\end{strip}
Once the relative flow of each stage, $F_{i}$, has been determined, the
cascade can be populated with actual machines up the stages
until either the maximum number available of machines or the maximum feed
flow is reached.

>>>>

The second step determines how to populate the cascade with the user-defined
maximum number of centrifuges. One first solves the linear flow equation to
determine the theoretical flow in the cascade.
%% 
%% \begin{strip}
%% \begin{equation}
%% \setcounter{MaxMatrixCols}{20}
%% \begin{bmatrix}
%% -1         & 1-\theta_{S+1} & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & 0            & 0 \\
%% \theta_{S} & -1             & 1-\theta_{S+2} & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & 0            & 0 \\
%%            &                &                &   &     &   &              & ... &                &   &     &              &              &   \\
%% 0          & 0              & 0              & 0 & ... & 0 & \theta_{-1}  & -1  & 1 - \theta_{1} & 0 & ... & 0            & 0            & 0 \\
%%            &                &                &   &     &   &              & ... &                &   &     &              &              &   \\
%% 0          & 0              & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & \theta_{E-2} & -1           & 1-\theta_{E} \\
%% 0          & 0              & 0              & 0 & ... & 0 & 0            & 0   & 0              & 0 & ... & 0            & \theta_{E-1} & -1
%% \end{bmatrix}
%% \times
%% \begin{bmatrix}
%%      F_{S}   \\
%%      F_{S+1} \\
%%      \cdots  \\
%%      F_{0}   \\
%%     \cdots   \\
%%     F_{E-1}  \\
%%     F_{E}
%% \end{bmatrix}
%% =
%% \begin{bmatrix}
%%      0   \\
%%      0 \\
%%      \cdots  \\
%%      F   \\
%%     \cdots   \\
%%     0  \\
%%     0
%% \end{bmatrix}
%% %\caption{caption needed!}
%% \label{eq:flow}
%% \end{equation}
%% \end{strip}
Once the relative flow of each stage has been determined, the
cascade can be populated with actual machines up the stages
until either the maximum number available of machines or the maximum feed
flow is reached.
